Meta-analysis of the Interoceptive Accuracy Scale

### 2025-01-29 analysis/study2.qmd
started average correlations analysis

>>>>

## Average Correlations

```{r}

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ (?), TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ (?), BPQ, MAIA, BRS (resilience?), PBCS (private bodily consciousness?)
# names(df5)
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
# names(df8a)  # EDI, BPQ
# names(df8b)  # TAS, PHQ15, PHQ9
# names(df9)  # BFI, STQ, EQ, ECR,
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10b)  # BDI, STAI, PHQ4
# names(df10c) # PI, MAIA
# names(df11a) # MAIA, TAS, MFQ(DEP), STAI(ANX)
# names(df11b)

# Compute total IAS scores for each dataset 
df1a$total_IAS <- rowSums(df1a[, c(3:23)])
```
